\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/experiments.tex
paper: inline ACS query

Our second set of queries is on the fCC data (\Cref{fig:queries-fcc}).
\Cref{q5} calculates the average income for survey participants, based on their bootcamp attendance.
\Cref{q6} estimates the average commute time of women from the United States who participated.
\Cref{q7} calculates the average amount of student debt based on school degree for survey participants who have student debt.
\Cref{q8} joins the freeCodeCamp data with a reference table provided by the World Bank which summarizes GDP per-capita across various countries~\cite{worldbank-data}.
The query calculates the average GDP per-capita of countries with and without bootcamp participants. 
\begin{table*}
\centering
 \begin{subtable}{\linewidth}
  \input{queries-cdc}
  \caption{Queries on CDC data}
  \label{fig:queries-cdc}
 \end{subtable}
 ~
 \begin{subtable}{\linewidth}
 \input{queries-fcc}
 \caption{Queries on fCC data}
 \label{fig:queries-fcc}
 \end{subtable}
 ~
 \begin{subtable}{\linewidth}
 \input{query-acs}
 \caption{Queries on ACS data}
 \label{fig:query-acs}
 \end{subtable}

  \caption{Queries used in our experiments.}
  \label{fig:queries}
\end{table*}

%\begin{table*}
%  \centerfloat
%  \input{runtimes}
%    \caption{Base error, percent change in error and and running time for queries
%    with different imputation levels. Base error is the root-mean-square error (RMSE) between the query run on clean
%    data and the query run on dirty data without imputation. Change in error is relative to the base error.}
%  \label{fig:experiments}
%\end{table*}

@@

\subsubsection{Runtime of Base-table Imputation}
In many real-world cases, applying the imputation step at the base table is prohibitively
expensive.
To illustrate the increasing difficulty of such an approach as datasets scale, we run~\Cref{q9} over the ACS dataset.
Applying the imputation operation to the base table is extremely expensive, in our case
completing in \acsbaseresultminutes (\Cref{fig:runtimes}. In contrast, \ProjectName{} executes a quality-optimized version
in\acsimputedbzeroresult~and a runtime-optimized version in \acsimputedboneresult. This highlights the potential
benefit of using our system for early data exploration.

>>>>

Our second set of queries is on the fCC data (\Cref{fig:queries-fcc}).
\Cref{q5} calculates the average income for survey participants, based on their bootcamp attendance.
\Cref{q6} estimates the average commute time of women from the United States who participated.
\Cref{q7} calculates the average amount of student debt based on school degree for survey participants who have student debt.
\Cref{q8} joins the freeCodeCamp data with a reference table provided by the World Bank which summarizes GDP per-capita across various countries~\cite{worldbank-data}.
The query calculates the average GDP per-capita of countries with and without bootcamp participants.

\begin{table*}
  \centering
  \begin{subtable}{\linewidth}
    \input{queries-cdc}
    \caption{Queries on CDC data}\label{fig:queries-cdc}
  \end{subtable}
  \par\medskip
  \begin{subtable}{\linewidth}
    \input{queries-fcc}
    \caption{Queries on fCC data}\label{fig:queries-fcc}
  \end{subtable}
  \par\medskip
  \caption{Queries used in our experiments.}\label{fig:queries}
\end{table*}

%\begin{table*}
%  \centerfloat
%  \input{runtimes}
%    \caption{Base error, percent change in error and and running time for queries
%    with different imputation levels. Base error is the root-mean-square error (RMSE) between the query on clean
%    data and the query run on dirty data without imputation. Change in error is relative to the base error.}
%  \label{fig:experiments}
%\end{table*}

@@

\subsubsection{Runtime of Base-table Imputation}
In many real-world cases, applying the imputation step at the base table is prohibitively
expensive.
To illustrate the increasing difficulty of such an approach as datasets scale, we ran the following query over the ACS dataset:
\begin{lstlisting}[breaklines]
SELECT AVG(c0) FROM acs_dirty;
\end{lstlisting}
Applying the imputation operation to the base table is extremely expensive, in our case
completing in \acsbaseresultminutes{} (\Cref{fig:runtimes}). In contrast, \ProjectName{} executes a quality-optimized version
in \acsimputedbzeroresult{} and a runtime-optimized version in \acsimputedboneresult{}. This highlights the potential
benefit of using our system for early data exploration.
